\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-09-05 paper/ms.tex
Some = signs should have been \sims
murray

\subsection{ABC example}
A simple ABC example is included in the directory
{\tt code/Examples/ABC}. The example tries to infer the mean
$\mu$ and standard deviation $\sigma$ of a normal distribution
from a set of samples. The sampling distribution is
\begin{align}
x_i &\sim \textnormal{Normal}(\mu, \sigma^2).
\end{align}
and the prior is
\begin{align}
\mu &\sim \textnormal{Uniform}(-10, 10)\\
\ln\sigma &= \textnormal{Uniform}(-10, 10).
\end{align}
However, instead of conditioning on the full dataset $\{x_i\}$, the example
uses the minimum and maximum values in the data,
$\min(\{x_i\})$ and $\max(\{x_i\})$, as summary statistics\footnote{This is
not a serious application of ABC, since the likelihood function can easily
be evaluated. It is included to demonstrate the principle of using
Nested Sampling as an ABC method.}.

@@

\begin{align}
\mu &\sim \textnormal{Uniform}(-10, 10)\\
\ln\sigma &= \textnormal{Uniform}(-10, 10)\\
n_i &= \textnormal{Normal}(0, 1)
\end{align}
where each of the $n_i$ enables a data point to be calculated using
\begin{align}
x_i &= \mu + \sigma n_i.
\end{align}
A general procedure for achieving this is to imagine generating a
simulated data set from the parameters. In this process, you would need
to call a random number generator many times.
The results of the random number calls
are independent of the parameters and
can be used to parameterize the data set. In the example,
the $\{n_i\}$ variables play this role.
Therefore, the variables in the model class are:
\begin{CodeChunk}
\begin{CodeInput}
class MyModel
{
    private:
        double mu, log_sigma;
        std::vector<double> n;
\end{CodeInput}
\end{CodeChunk}

@@

\section*{Acknowledgements}
John Veitch (Birmingham)
and Jorge Alarcon Ochoa (Rensselaer Polytechnic Institute)
provided helpful comments on an early
version of the manuscript.
It is a pleasure to thank Anna Pancoast (Harvard),
Ewan Cameron (Oxford), David Hogg (NYU), and Daniela Huppenkothen (NYU)
for valuable discussions. BJB was supported by a Marsden Fast-Start grant
from the Royal Society of New Zealand.

>>>>

\subsection{ABC example}
A simple ABC example is included in the directory
{\tt code/Examples/ABC}. The example tries to infer the mean
$\mu$ and standard deviation $\sigma$ of a normal distribution
from a set of samples. The sampling distribution is
\begin{align}
x_i &\sim \textnormal{Normal}(\mu, \sigma^2).
\end{align}
and the prior is
\begin{align}
\mu &\sim \textnormal{Uniform}(-10, 10)\\
\ln\sigma &\sim \textnormal{Uniform}(-10, 10).
\end{align}
However, instead of conditioning on the full dataset $\{x_i\}$, the example
uses the minimum and maximum values in the data,
$\min(\{x_i\})$ and $\max(\{x_i\})$, as summary statistics\footnote{This is
not a serious application of ABC, since the likelihood function can easily
be evaluated. It is included to demonstrate the principle of using
Nested Sampling as an ABC method.}.

@@

\begin{align}
\mu &\sim \textnormal{Uniform}(-10, 10)\\
\ln\sigma &\sim \textnormal{Uniform}(-10, 10)\\
n_i &\sim \textnormal{Normal}(0, 1)
\end{align}
where each of the $n_i$ enables a data point to be calculated using
\begin{align}
x_i &:= \mu + \sigma n_i.
\end{align}
A general procedure for achieving this is to imagine generating a
simulated data set from the parameters. In this process, you would need
to call a random number generator many times.
The results of the random number calls
are independent of the parameters and
can be used to parameterize the data set. In the example,
the $\{n_i\}$ variables play this role.
Therefore, the variables in the model class are:
\begin{CodeChunk}
\begin{CodeInput}
class MyModel
{
    private:
        double mu, log_sigma;
        std::vector<double> n;
\end{CodeInput}
\end{CodeChunk}

@@

\section*{Acknowledgements}
John Veitch (Birmingham)
and Jorge Alarcon Ochoa (Rensselaer Polytechnic Institute)
provided helpful comments on an early
version of the manuscript.
It is a pleasure to thank Anna Pancoast (Harvard),
Ewan Cameron (Oxford), David Hogg (NYU), Daniela Huppenkothen (NYU),
and Iain Murray (Edinburgh)
for valuable discussions. This work was supported by a Marsden Fast-Start grant
from the Royal Society of New Zealand.
